Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-02 analysis/paper/hotspots-paper.Rmd
added quotes around {{keller_mediator}} to fix compilation

```{r setup_continued}
hot_chr <- c(2, 5, 7, 11, 13)
hot_mid <- c(165.5, 146, 46, 71, 112.5)
keller_mediator <- c("Hnf4a", "Pdx1", "Fam83e", "Sat2", "Il6st")
out <- pmap(tibble(hot_chr, hot_mid, keller_mediator), .f = function(hot_chr, hot_mid, keller_mediator) knitr::knit_expand(text = readLines(here::here("analysis", "paper", "hotspot-one-chromosome.Rmd"))))
# note that ... argument must be a list, ie, it must be a single argument, not multiple args
```

>>>>

```{r setup_continued}
hot_chr <- c(2, 5, 7, 11, 13)
hot_mid <- c(165.5, 146, 46, 71, 112.5)
keller_mediator <- c("Hnf4a", "Pdx1", "Fam83e", "Sat2", "Il6st")
inputs <- tibble(hot_chr, hot_mid, keller_mediator)
out <- pmap_dfc(inputs, .f = function(hot_chr, hot_mid, keller_mediator) knitr::knit_expand(text = readLines(here::here("analysis", "paper", "hotspot-one-chromosome.Rmd"))))
# note that ... argument must be a list, ie, it must be a single argument, not multiple args
```
